### 2018-05-18 paper/paper.tex
minor updates to bayesian analysis

The model provided evidence for the predicted effect of the discourse status of the generalization on the at-issueness of the prejacent, such that  prejacents of EASs with generalizations that follow from the common ground were more likely to receive a `yes' rating than prejacents of EASs with neutral generalizations  ($\beta$ = \jt{???}, 95\% Credible Interval={[}\jt{??, ??}{]}).\footnote{In Bayesian mixed effects regression modeling, 95\% credible intervals indicate the range within which we can be certain with probability 0.95 that the parameter estimate $\beta$  lies, given the data at hand and our model (see, for example, Jaynes \& Kempthorne,1976;  Morey, Hoekstra, Rouder, Lee, \& Wagenmakers, 2016).\jd{JT, I'm unsure about how much info to include here and will add citations depending on what we decide to include}} This finding suggests that the prejacent of EASs with generalizations that follow from the common ground are more at-issue than that of EASs with neutral generalizations. 
%We fitted a binomial mixed-effects logistic regression predicting rating (0/no, 1/yes) from a fixed effect of condition (with EAS$_{\mbox{n}}$ as the reference level; 680 data points). The model included the maximal random effects structure justified by the data that allowed the model to converge: random by-adjective intercepts (capturing differences in at-issueness between adjectives).\footnote{A model that predicted rating from condition with a random by-participant intercept (capturing differences in at-issueness rating between participants) also revealed a main effect of condition ($\beta$ = 1.23, $SE$ = 0.23, $z$ = 5.32, $\chi^2$(1) = 27.62, $p <$ .0001).} The analysis was conducted using the lme4 package (\citealt{bates-etal2015}). A log-likelihood comparison of the model with the fixed effect to the model without the fixed effect revealed a significant main effect of EAS type. Specifically, the prejacent of EAS$_{\mbox{f}}$ received more `yes' ratings than the prejacent of EAS$_{\mbox{n}}$ ($\beta$ = 0.56, $SE$ = 0.16, $z$ = 3.57, $\chi^2$(1) = 12.89, $p =$ .0003), indicating that the prejacent of EAS$_{\mbox{f}}$ was judged to be more at-issue than that of EAS$_{\mbox{n}}$. 
These findings provide empirical support for the analysis developed in section \ref{s3}, which predicts that the prejacent of EASs is more likely to be at-issue when the generalization follows from the common ground than when it does not.\footnote{The projective content of the four control stimuli in (\ref{proj}) differed in the extent to which they received `no' ratings (indicating not-at-issueness): 94\% (64 of 68) for the appositive content in (\ref{proj}a), 90\% (61 of 68 for the possession content in (\ref{proj}b), 75\% (51 of 68) for the content of the clausal complement of {\em be annoyed} in (\ref{proj}c) and 44\% (30 of 68) for the content of the clausal complement of {\em discover} in (\ref{proj}d). We can compare these findings with the findings reported for similar contents in \citealt{tbd-variability}, whose Exp.~2a used the same diagnostic for at-issueness, but participants gave ratings on a slider. Further differences between the two experiments is that \citealt{tbd-variability} included more than one item for each of the projective contents but only included EASs with {\em stupid}. With these caveats in mind, we can note a similarity in the findings of the two experiments: as in the experiment reported on here, \citet{tbd-variability} found that the possession content and appositive content were most not-at-issue (mean ratings of .83 and .82, respectively), followed by the content of the clausal complement of {\em be annoyed} (mean: .78) and the prejacent of EASs (mean: .7), and finally the content of the clausal complement of {\em discover} (mean .47). These findings provide further support for the hypothesis that the prejacent of EASs overall is not highly not-at-issue.}

>>>>

The model provided evidence for the predicted effect of the discourse status of the generalization on the at-issueness of the prejacent, such that  prejacents of EASs with generalizations that follow from the common ground were more likely to receive a `yes' rating than prejacents of EASs with neutral generalizations  ($\beta$ = 1.29, 95\% Credible Interval={[}0.69,1.87{]}).\footnote{In Bayesian mixed effects regression modeling, 95\% credible intervals indicate the range within which we can be certain with probability 0.95 that the parameter estimate $\beta$  lies, given the data at hand and our model (see, for example, Jaynes \& Kempthorne,1976;  Morey, Hoekstra, Rouder, Lee, \& Wagenmakers, 2016).\jd{JT, I'm unsure about how much info to include here and will add citations depending on what we decide to include}} This finding suggests that the prejacent of EASs with generalizations that follow from the common ground are more at-issue than that of EASs with neutral generalizations. 
%We fitted a binomial mixed-effects logistic regression predicting rating (0/no, 1/yes) from a fixed effect of condition (with EAS$_{\mbox{n}}$ as the reference level; 680 data points). The model included the maximal random effects structure justified by the data that allowed the model to converge: random by-adjective intercepts (capturing differences in at-issueness between adjectives).\footnote{A model that predicted rating from condition with a random by-participant intercept (capturing differences in at-issueness rating between participants) also revealed a main effect of condition ($\beta$ = 1.23, $SE$ = 0.23, $z$ = 5.32, $\chi^2$(1) = 27.62, $p <$ .0001).} The analysis was conducted using the lme4 package (\citealt{bates-etal2015}). A log-likelihood comparison of the model with the fixed effect to the model without the fixed effect revealed a significant main effect of EAS type. Specifically, the prejacent of EAS$_{\mbox{f}}$ received more `yes' ratings than the prejacent of EAS$_{\mbox{n}}$ ($\beta$ = 0.56, $SE$ = 0.16, $z$ = 3.57, $\chi^2$(1) = 12.89, $p =$ .0003), indicating that the prejacent of EAS$_{\mbox{f}}$ was judged to be more at-issue than that of EAS$_{\mbox{n}}$. 
These findings provide empirical support for the analysis developed in section \ref{s3}, which predicts that the prejacent of EASs is more likely to be at-issue when the generalization follows from the common ground than when it does not.\footnote{The projective content of the four control stimuli in (\ref{proj}) differed in the extent to which they received `no' ratings (indicating not-at-issueness): 94\% (64 of 68) for the appositive content in (\ref{proj}a), 90\% (61 of 68 for the possession content in (\ref{proj}b), 75\% (51 of 68) for the content of the clausal complement of {\em be annoyed} in (\ref{proj}c) and 44\% (30 of 68) for the content of the clausal complement of {\em discover} in (\ref{proj}d). We can compare these findings with the findings reported for similar contents in \citealt{tbd-variability}, whose Exp.~2a used the same diagnostic for at-issueness, but participants gave ratings on a slider. Further differences between the two experiments is that \citealt{tbd-variability} included more than one item for each of the projective contents but only included EASs with {\em stupid}. With these caveats in mind, we can note a similarity in the findings of the two experiments: as in the experiment reported on here, \citet{tbd-variability} found that the possession content and appositive content were most not-at-issue (mean ratings of .83 and .82, respectively), followed by the content of the clausal complement of {\em be annoyed} (mean: .78) and the prejacent of EASs (mean: .7), and finally the content of the clausal complement of {\em discover} (mean .47). These findings provide further support for the hypothesis that the prejacent of EASs overall is not highly not-at-issue.}
